Annotated example of index standardization with inlabru

### 2021-11-18 doc/appendix-pcod-inlabru.Rmd
Fix a few small things; run styler

spde <- inla.spde2.pcmatern(mesh = mesh$mesh,
                            prior.range = c(10, 0.05), # P(range < 10) = 0.05
                            prior.sigma = c(2, 0.05)) # P(sigma > 2) = 0.05
```

@@

```{r}
sdmtmb_fit <- sdmTMB(present ~ -1 + as.factor(year), data = pcod,
   time = "year", spde = mesh, 
   family = binomial(link="logit"), 
   spatial_only=TRUE,
   priors = sdmTMBpriors(
                      matern_st = pc_matern(range_gt = 10, range_prob = 0.05,
                                            sigma_lt = 2, sigma_prob = 0.05)
                    ))
sdmtmb_coefs = tidy(sdmtmb_fit, effects="fixed")
```

@@

```{r fit-pcod, warning=FALSE, message=FALSE}
m <- lm(present ~ -1 + as.factor(year), data = pcod)
model_mat = model.matrix(m)
colnames(model_mat) = paste0("x",unique(pcod$year))
dat <- cbind(pcod, model_mat)
```

@@

```{r}
components <- present ~ -1 + x2003 + x2004 + x2005 + x2007 +
  x2009 + x2011 + x2013 + x2015 + x2017 +
  spatrf(main = coordinates,model = spde) + 
  #spatrf(main = coordinates,model = spde, group=year, ngroup=ncol(model_mat),
  #       control.group = list(model = "iid"))

fit <- bru(components = components,
             family = "binomial", data = dat)
bru_coefs <- fit$summary.fixed[,c("mean","sd")]
```

@@

```{r}
plot(sdmtmb_coefs$estimate, bru_coefs$mean)
```

@@

```{r}
components <- present ~ 0 +
  fac(main = year, model = "factor_full") + 
  spatrf(main = coordinates,model = spde)

fit2 <- bru(components = components,
             family = "binomial", data = dat)
bru_coefs2 <- fit2$summary.random$fac[,c("mean","sd")]
```

>>>>

spde <- inla.spde2.pcmatern(
  mesh = mesh$mesh,
  prior.range = c(10, 0.05), # P(range < 10) = 0.05
  prior.sigma = c(2, 0.05)
) # P(sigma > 2) = 0.05
```

@@

```{r}
sdmtmb_fit <- sdmTMB(present ~ -1 + as.factor(year),
  data = pcod,
  time = "year", spde = mesh,
  family = binomial(link = "logit"),
  spatiotemporal = "off",
  priors = sdmTMBpriors(
    matern_st = pc_matern(
      range_gt = 10, range_prob = 0.05,
      sigma_lt = 2, sigma_prob = 0.05
    )
  )
)
sdmtmb_coefs <- tidy(sdmtmb_fit, effects = "fixed")
```

@@

```{r fit-pcod, warning=FALSE, message=FALSE}
m <- lm(present ~ -1 + as.factor(year), data = pcod)
model_mat <- model.matrix(m)
colnames(model_mat) <- paste0("x", unique(pcod$year))
dat <- cbind(pcod, model_mat)
```

@@

```{r}
components <- present ~ -1 + x2003 + x2004 + x2005 + x2007 +
  x2009 + x2011 + x2013 + x2015 + x2017 +
  spatrf(main = coordinates, model = spde)
# spatrf(main = coordinates,model = spde, group=year, ngroup=ncol(model_mat),
#       control.group = list(model = "iid"))

fit <- bru(
  components = components,
  family = "binomial", data = dat
)
bru_coefs <- fit$summary.fixed[, c("mean", "sd")]
```

@@

```{r}
plot(sdmtmb_coefs$estimate, bru_coefs$mean)
abline(a = 0, b = 1)
```

@@

```{r}
components <- present ~ 0 +
  fac(main = year, model = "factor_full") +
  spatrf(main = coordinates, model = spde)

fit2 <- bru(
  components = components,
  family = "binomial", data = dat
)
bru_coefs2 <- fit2$summary.random$fac[, c("mean", "sd")]
```
